---
title: "imit_models"
author: "Astrid L."
date: "19/11/2018"
output: html_document
---


TO DO 
Define hypotheses / Describe variables
- Identify your model (outcome, likelihood function, predictors)
- Identify submodels for comparison
Define and motivate your priors 
- (predictive prior distribution?)
Assess model quality
- WAIC comparison
- Estimate comparison
- Predictive posterior
Report results
- Estimates and estimate interpretation
- Make sure to deal cautiously with interactions (e.g. plot!)
Compare current state of knowledge with previous
- E.g. prior vs. Posterior estimates


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# (package that helps model converge: optimX)
library(nloptr)
library(lme4)
install.package(nloptr)
install.packages("nloptr")
add this argument:
control=glmerControl(optimizer="nloptwrap2"))

getwd()
locpath= getwd()
setwd(locpath)

library(pacman)
#p_load(ggplot2, rethinking, readxl, brms, metafor, tidyverse, lme4, Rstan)
p_load(ggplot2, tidyverse, lme4, dplyr, lmerTest, data.table, dtplyr, effects, MuMin)

d_IRI <- read.csv("~/Desktop/Bachelor/BA_EXP/d_IRI.csv")
d_all_ii <- read.csv("~/Desktop/Bachelor/BA_EXP/all_ii_new.csv", header = TRUE) 

# merging datasets
d <- merge(d_all_ii,d_IRI,by="Participant")
# writing to csv file
#setwd("~/Desktop/Bachelor/BA_EXP/")
#write.csv(d, file = "d.csv", row.names=FALSE)

# variables
d$Condition = as.factor(d$Condition)
d$Gender = as.character(d$Gender)
d$Gender[d$Gender == "1"] = "male"
d$Gender[d$Gender == "0"] = "female"
d$Gender = as.factor(d$Gender)
d$Correctness = as.factor(d$Correctness)
# ordering factors (e.g. For Condition, it would be good if IT was the baseline, or first category, because then we would know that the model coefficients reflect the probability of being cured (which is what we want to know) rather than the probability of not being cured.”
d$Condition <- relevel(d$Condition, "IT")

str(d)
mean(d$Age)
sd(d$Age)
# removing negative reaction times
#d$Reaction_time[d$Reaction_time < 0] = 'nan'

```


# visualizing data
```{r}
rt = ggplot(d,aes(Reaction_time))+geom_density()
print(rt)

#log transform
d$RTlog=log(d$Reaction_time)
rtlog = ggplot(d,aes(RTlog))+geom_density()
print(rtlog)

#boxplot(Reaction_time ~ Congruity, main="results for the effect on reaction_time", d)
# winning or losing rate of acceptance 
team_cond_rate = data1 %>%
  group_by(d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '1'))
team_cond_rate
```

ordering data
# remove negative RTs
# scale RTs
# remove incorrect trials
# make subset with means for participants 
```{r}
d$Reaction_time[d$Reaction_time < 0] = 'nan'
d = d[complete.cases(d),] 

d$Reaction_time = as.numeric(d$Reaction_time)
class(d$Reaction_time)
d$RT_s = scale(d$Reaction_time, center = TRUE, scale = TRUE)
d_s = as.data.frame(d_s)

d$Correctness[d$Correctness == 0] = 'nan'
d = d[complete.cases(d),] 

d$Participant

d$Item = paste(d$Cue, d$Finger)
d$Item = as.factor(d$Item)

d$FS_s = scale(d$FS, center = TRUE, scale = TRUE)
d$EC_s = scale(d$EC, center = TRUE, scale = TRUE)
d$PT_s = scale(d$PT, center = TRUE, scale = TRUE)
d$PD_s = scale(d$PD, center = TRUE, scale = TRUE)
d$SS_s = scale(d$SS, center = TRUE, scale = TRUE)

#
d_incongruent <- education[-c(1:9,22:50),-c(1,3:5)]
d$Congruity = as.character(d$Congruity)
class(d$Congruity)
d_incongruent <- subset(d, d$Congruity == "No", )

# d_all = dataset with all variables scaled and not, d = original non-scaled variables, d_s = relevant columns are scaled  
#1990 24
#d_all <- d[,]
#d <- d[, -c(18,20,21,22,23,24)] 
d_1 = data.frame(d$Participant, d$V1, d$Condition, d$Congruity, d$Response, d$Correctness, d$Cue, d$Finger, d$Item, d$Gender) # RT_log?
d_s <- d[, c(5, 10,11,12,13,14,16)] 
# standardizing the data (centering and scaling)
d_s = scale(d_s, center = TRUE, scale = TRUE)
d_s = as.data.frame(d_s)
# new data frame
d_s = cbind(d_1, d_s)

# renaming variables 
####### apparently this won't work
#plyr::rename(d_s, c("d.Participant"="Participant", "d.V1"="V1", "d.Condition"="Condition", "d.Congruity"="Congruity", "d.Response"="Response", "d.Correctness"="Correctness", "d.Cue"="Cue", "d.Finger"="Finger", "d.Item"="Item", "d.Gender"="Gender"))

names(d_s)[names(d_s) == "d.Participant"] <- "Participant"
names(d_s)[names(d_s) == "d.V1"] <- "V1"
names(d_s)[names(d_s) == "d.Condition"] <- "Condition"
names(d_s)[names(d_s) == "d.Congruity"] <- "Congruity"
names(d_s)[names(d_s) == "d.Response"] <- "Response"
names(d_s)[names(d_s) == "d.Correctness"] <- "Correctness"
names(d_s)[names(d_s) == "d.Cue"] <- "Cue"
names(d_s)[names(d_s) == "d.Finger"] <- "Finger"
names(d_s)[names(d_s) == "d.Item"] <- "Item"
names(d_s)[names(d_s) == "d.Gender"] <- "Gender"

# writing to csv file
write.csv(d_s, file = "d_s.csv", row.names=FALSE)
d_s <- read.csv("~/Desktop/Bachelor/BA_EXP/d_s.csv", header = TRUE) 

write.csv(d, file = "d.csv", row.names=FALSE)
d <- read.csv("~/Desktop/Bachelor/BA_EXP/d.csv", header = TRUE) 

write.csv(d_all, file = "d_all.csv", row.names=FALSE)
d_all <- read.csv("~/Desktop/Bachelor/BA_EXP/d_all.csv", header =  TRUE)

##
```

# Pipes
```{r}
# PIPES 
str(d)
library(tidyverse)
library(dplyr)
library(plyr)
d$Congruity = as.factor(d$Congruity)
# variables should be factors to function in ggplot

```

Hypotheses 

# H1:  Imitation inhibition training improve performance on a subsequent cued control task
	P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.

# H2:  Imitation inhibition training improve subsequent measures of social cognition
Hypothesis 2 motivates two complementary predictions:
	P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition.
	P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.

# Planned exploratory analyses	
-	EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot)
-	EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance

scale subscores + ss
# models
```{r}
## H1:  Imitation inhibition training improve performance on a subsequent cued control task

# P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.
m1 = glmer(Reaction_time ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), family=gaussian(link=log), data = d)
summary(m1)
qqnorm(residuals(m1))
dpois
# Visualization
ggplot(d, aes(Condition, Reaction_time, fill = Congruity)) + 
  geom_bar(stat = "summary", fun.y = mean, position = "dodge", width = 0.6) + 
  geom_errorbar(stat = "summary", fun.data = mean_se, position = "dodge", width = 0.4)

#m1.2 = lmer(log(Reaction_time) ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), data = d, REML = FALSE)
#summary(m1.2)
#qqnorm(residuals(m1.2))

## H2:  Imitation inhibition training improve subsequent measures of social cognition
#(Hypothesis 2 motivates two complementary predictions:)

# P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition. 
m2 = glmer(Condition ~ 1 + FS_s + EC_s + PT_s + PD_s + (1|Participant), family=binomial, data=d)
summary(m2)


# P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.
m3 = glmer(Condition ~ 1 + SS_s + (1|Participant), family=binomial, data=d)
summary(m3)

## Planned exploratory analyses	
# EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot) (choose congruent/incongruent only??)
ea1 = glmer(Condition ~ 1 + RT_s + EC_s + RT_s*EC_s + (1|Participant), family=binomial, data=d_incongruent)
summary(ea1)

# EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance.
ea2 = glmer(Condition ~ 1 + FS_s + EC_s + PT_s + PD_s + SS_s + (1|Participant), family=binomial, data=d)
summary(ea2)

```

```{r}
str(d)
d$Correctness_fac <-factor(d$Correctness) #change variable into factor


#check RT
rt = ggplot(d,aes(Reaction_time))+geom_density()
print(rt)
#log transform

d$RTlog=log(d$Reaction_time)
rtlog = ggplot(d,aes(RTlog))+geom_density()
print(rtlog)

#m = lm(Condition ~ 1 + FS + EC + PT + PD + SS, data = d)

model21 = glmer(Correctness~Congruity+(1+Congruity|Participant)+(1+Congruity|Cue),family =binomial,d)
model1_2 = glmer(Correctness ~ Congruity + (1 + Congruity|Participant) + (1 + Congruity|Cue),family =binomial,d)
summary(model1_2)

#group by correctness (finger/congruity)
all_correctness = d %>%
  group_by(Participant, Congruity, Cue) %>%
  summarise(Number_correct=sum(Correctness))

```

# Questions
```{r}


```

# Pipes
```{r}
library("dplyr")

# looking at Condition and SS score
cond_SS_sum = d %>%
  group_by(Condition == 'II') %>% 
   summarise(SSscore = mean(SS))
cond_SS_sum
# very similar regardless of Condition
# boxplot
p1 <- ggplot(data=d, aes(x = Condition, y = SS)) +
  geom_boxplot() +
  labs(title = "Effect of condition on SS score", x = "Condition", y = "SS score")
p1

# looking at Condition and RT on CT
cond_RT_sum = d %>%
  group_by(Condition == 'II') %>% 
   summarise(RT = mean(Reaction_time))
cond_RT_sum
# there is a minor difference
# boxplot
p2 <- ggplot(data=d, aes(x = Condition, y = Reaction_time)) +
  geom_boxplot() + 
  labs(title = "Effect of condition on RTs", x = "Condition", y = "Mean RTs")
p2



```

