---
title: "latest_ba_models"
author: "Astrid L."
date: "28/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

# install.packages("nloptr")
# add this argument:
# control=glmerControl(optimizer="nloptwrap2"))

getwd()
locpath= getwd()
setwd(locpath)

library(pacman)
#p_load(ggplot2, rethinking, readxl, brms, metafor, tidyverse, lme4, Rstan)
p_load(ggplot2, tidyverse, lme4, dplyr, lmerTest, data.table, dtplyr, effects, MuMin, plyr)

d_s <- read.csv("~/Desktop/Bachelor/BA_EXP/d_s.csv", header = TRUE) # scaled variables
d <- read.csv("~/Desktop/Bachelor/BA_EXP/d.csv", header = TRUE) # original variables
# d_all <- read.csv("~/Desktop/Bachelor/BA_EXP/d_all.csv", header =  TRUE) # both

# updating dataset
d_s <- subset(d_s, select = -c(Correctness))
d_s$Condition <- relevel(d_s$Condition, "IT")

str(d_s)
d_s$Congruity = as.character(d$Congruity)
d_incongruent_s <- subset(d_s, d_s$Congruity == "No")
d_s$Congruity = as.factor(d_s$Congruity)
str(d_incongruent_s)

```


# Descriptive data
```{r}
mean(d$Age)
sd(d$Age)
```


# Visualizing data
```{r}

rt = ggplot(d_s,aes(Reaction_time))+geom_density()
rt = ggplot(d,aes(Reaction_time))+geom_density()
rt

# Boxplot
# Effect of condition and congruity on reacion times
a <- ggplot(data=d_s, aes(x = Condition, y = Reaction_time, colour = d_s$Congruity)) +
  geom_boxplot() +
  labs(title = "Effect of condition and congruity on reacion times", x = "Condition", y = "Scaled RTs", colour = "Congruity")
a

# condition and congruity switched around 
a_1 <- ggplot(data=d_s, aes(x = Congruity, y = Reaction_time, colour = d_s$Condition)) +
   geom_boxplot() +
   labs(title = "Effect of congruity and condition on reacion times", x = "Congruity", y = "Scaled RTs", colour = "Condition")
a_1

# barplot
# Effect of condition and congruity on reacion times
b <- ggplot(data=d_s, aes(x = Condition, y = Reaction_time, colour = d_s$Congruity)) +
  geom_bar() +
  labs(title = "Effect of condition and congruity on reacion times", x = "Condition", y = "Scaled RTs", colour = "Congruity")
b

```

Hypotheses 

# H1:  Imitation inhibition training improve performance on a subsequent cued control task
	P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.

# H2:  Imitation inhibition training improve subsequent measures of social cognition
Hypothesis 2 motivates two complementary predictions:
	P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition.
	P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.

# Planned exploratory analyses	
-	EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot)
-	EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance


```{r}
## H1:  Imitation inhibition training improve performance on a subsequent cued control task

# P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.
m1 = glmer(Reaction_time ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), family=gaussian(link=log), data = d)
summary(m1)
qqnorm(residuals(m1))
dpois
# Visualization
ggplot(d, aes(Condition, Reaction_time, fill = Congruity)) + 
  geom_bar(stat = "summary", fun.y = mean, position = "dodge", width = 0.6) + 
  geom_errorbar(stat = "summary", fun.data = mean_se, position = "dodge", width = 0.4)

#m1.2 = lmer(log(Reaction_time) ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), data = d, REML = FALSE)
#summary(m1.2)
#qqnorm(residuals(m1.2))

## H2:  Imitation inhibition training improve subsequent measures of social cognition
#(Hypothesis 2 motivates two complementary predictions:)

# P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition. 
m2 = glmer(Condition ~ 1 + FS_s + EC_s + PT_s + PD_s + (1|Participant), family=binomial, data=d)
summary(m2)


# P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.
m3 = glmer(Condition ~ 1 + SS_s + (1|Participant), family=binomial, data=d)
summary(m3)

## Planned exploratory analyses	
# EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot) (choose congruent/incongruent only??)
ea1 = glmer(Condition ~ 1 + RT_s + EC_s + RT_s*EC_s + (1|Participant), family=binomial, data=d_incongruent)
summary(ea1)

# EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance.
ea2 = glmer(Condition ~ 1 + FS_s + EC_s + PT_s + PD_s + SS_s + (1|Participant), family=binomial, data=d)
summary(ea2)

```


