---
title: "latest_ba_models"
author: "Astrid L."
date: "28/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

# install.packages("nloptr")
# add this argument:
# control=glmerControl(optimizer="nloptwrap2"))

getwd()
locpath= getwd()
setwd(locpath)

library(pacman)
p_load(ggplot2, tidyverse, lme4, dplyr, lmerTest, data.table, dtplyr, effects, MuMin, plyr, brms, Rstan, rethinking, metafor)

# this is the updated data
d <- read.csv("~/Desktop/Bachelor/BA_EXP/d.csv", header = TRUE) 
d_s <- read.csv("~/Desktop/Bachelor/BA_EXP/d_s.csv", header = TRUE) 
d_incongruent <- read.csv("~/Desktop/Bachelor/BA_EXP/d_incongruent.csv", header =  TRUE)
d_incongruent_s <- read.csv("~/Desktop/Bachelor/BA_EXP/d_incongruent_s.csv", header =  TRUE)


# updating levels
d$Condition <- relevel(d$Condition, "IT")
d_s$Condition <- relevel(d_s$Condition, "IT")
d_incongruent$Condition <- relevel(d_incongruent$Condition, "IT")
d_incongruent_s$Condition <- relevel(d_incongruent_s$Condition, "IT")

# exploring distribution of rt
rt = ggplot(d,aes(RTlog))+geom_density()
print(rt)

```


# Descriptive data
```{r}
mean(d$Age)
sd(d$Age)
```


# Visualizing data
```{r}
#rt = ggplot(d_s,aes(Reaction_time))+geom_density()
#rt = ggplot(d,aes(Reaction_time))+geom_density()
#rt

##### H1 ###### (P1)
# Boxplot
# Effect of condition and congruity on reacion times
p1_a <- ggplot(data=d_s, aes(x = Condition, y = Reaction_time, colour = d_s$Congruity)) +
  geom_boxplot() +
  labs(title = "Effect of condition and congruity on reacion times", x = "Condition", y = "Scaled RTs", colour = "Congruity")
p1_a

# condition and congruity switched around 
p1_b <- ggplot(data=d_s, aes(x = Congruity, y = Reaction_time, colour = d_s$Condition)) +
   geom_boxplot() +
   labs(title = "Effect of congruity and condition on reacion times", x = "Congruity", y = "Scaled RTs", colour = "Condition")
p1_b

# barplot 
# Not scaled! Effect of condition and congruity on reacion times
p1_c <- ggplot(d, aes(Condition, Reaction_time, fill = Congruity)) + 
  geom_bar(stat = "summary", fun.y = mean, position = "dodge", width = 0.7) + 
  geom_errorbar(stat = "summary", fun.data = mean_se, position = "dodge", width = 0.4) +
  labs(title = "Effect of condition and congruity on reacion times", x = "Condition", y = "Reaction time", colour = "Congruity")
p1_c

# Scaled! Effect of condition and congruity on reacion times
p1_d <- ggplot(d_s, aes(Condition, Reaction_time, fill = Congruity)) +
  geom_bar(stat = "summary", fun.y = mean, position = "dodge", width = 0.7) +
  geom_errorbar(stat = "summary", fun.data = mean_se, position = "dodge", width = 0.4) +
  labs(title = "Effect of condition and congruity on reacion times", x = "Condition", y = "Scaled RTs", colour = "Congruity")
p1_d


##### H2 ###### (P2 & P3)
# install.packages("gridExtra")
library(gridExtra)

# FS (I will use the scaled IRI scores bc it is an arbitrary scale otherwise)
p2_a <- ggplot(data=d_s, aes(x = Condition, y = FS)) +
   geom_boxplot() +
   labs(title = "Fantasy", x = "Condition", y = "Scaled FS score")
p2_a
# EC
p2_b <- ggplot(data=d_s, aes(x = Condition, y = EC)) +
   geom_boxplot() +
   labs(title = "Empathic Concern", x = "Condition", y = "Scaled EC score")
p2_b
# PT
p2_c <- ggplot(data=d_s, aes(x = Condition, y = PT)) +
   geom_boxplot() +
   labs(title = "Perspective Taking", x = "Condition", y = "Scaled PT score")
p2_c
# PD 
p2_d <- ggplot(data=d_s, aes(x = Condition, y = PD)) +
   geom_boxplot() +
   labs(title = "Personal Distress", x = "Condition", y = "Scaled PD score")
p2_d

# All combined
p2_e <- grid.arrange(p2_a, p2_b, p2_c, p2_d, ncol=4)

p3_a<- ggplot(data=d_s, aes(x = Condition, y = SS)) +
   geom_boxplot() +
   labs(title = "Social Sensitivity", x = "Condition", y = "Scaled SS score")
p3_a

# maybe all plots together?
p3_b <- grid.arrange(p2_a, p2_b, p2_c, p2_d, p3_a, ncol=5)


##### EA ###### (EA1 & EA2)
p4_a <- ggplot(d_incongruent_s, aes(x=EC, y=Reaction_time, color=Condition)) + 
  geom_point() + geom_smooth(method = "lm") + labs(x = "Empathic Concern", y = "Reaction Time", title = "Reaction time, EC, and Condition")
p4_a


```

Hypotheses 

# H1:  Imitation inhibition training improve performance on a subsequent cued control task
	P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.

# H2:  Imitation inhibition training improve subsequent measures of social cognition
Hypothesis 2 motivates two complementary predictions:
	P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition.
	P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.

# Planned exploratory analyses	
-	EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot)
-	EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance


```{r}
## H1:  Imitation inhibition training improve performance on a subsequent cued control task

# P1 – Following the hypothesis 1, I predict to observe lower RTs on incongruent trials for participants in the imitation inhibition condition, giving rise to an interaction effect between condition and congruency.
m1 = lmer(RTlog ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), data = d, REML = FALSE)
summary(m1.1)
qqnorm(residuals(m1.1))

m1.1 = glmer(Reaction_time ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), family=gaussian(link = "log"), data = d)
summary(m1)
qqnorm(residuals(m1))

m1.2 = glmer(Reaction_time ~ Condition + Congruity + Condition*Congruity + (1|Participant) + (1|Item), family=poisson(link = "log"), data = d) # complaining / creating warnings bc RTs are not integers
summary(m1.2)
# random effects: both systematic variabce and randomm variance in... variable (slope|intercept)


## H2:  Imitation inhibition training improve subsequent measures of social cognition
#(Hypothesis 2 motivates two complementary predictions:)

# P2 – Subscale scores on the Interpersonal Reactivity Index are predictive of condition, with higher scores in the imitation inhibition condition. 
m2 = glmer(Condition ~ 1 + FS + EC + PT + PD + (1|Participant), family=binomial, data=d_s)
summary(m2)

r.squaredGLMM(m2) # this number explains how much of the variance is explained by the model (in this case 0.35 = 35%)???


# P3 – Social sensitivity scores from Reading the Mind in the Eyes Test (RMET) are predictive of condition, with higher scores in the imitation inhibition condition.
m3 = glmer(Condition ~ 1 + SS + (1|Participant), family=binomial, data=d_s)
summary(m3)

## Planned exploratory analyses	
# EA1 Explore the interaction effect between RTs on incongruent trials and specific subscales of the Interpersonal Reactivity Index.  (scatterplot) (choose congruent/incongruent only??)
ea1 = glmer(Condition ~ 1 + Reaction_time + EC + Reaction_time*EC + (1|Participant), family=binomial, data=d_incongruent_s)
summary(ea1)

ea1.1 = glmer(Condition ~ 1 + Reaction_time + PT + Reaction_time*PT + (1|Participant), family=binomial, data=d_incongruent_s)
summary(ea1.1)

#ea1.2 = glmer(Condition ~ 1 + EC + PT + EC*PT + (1|Participant), family=binomial, data=d_s)
#summary(ea1.2)
#r.squaredGLMM(ea1.2) # this number explains how much of the variance is explained by the model (in this case 0.35 = 35%)???

# EA2 Explore model including all measured variables of social cognition to see if they account for orthogonal variance.
ea2 = glmer(Condition ~ 1 + FS + EC + PT + PD + SS + (1|Participant), family=binomial, data=d_s)
summary(ea2)
r.squaredGLMM(ea2) 
cor(d_s$EC, d_s$PT)

# not really supposed to do this model 
ea2.1 = glmer(Condition ~ 1 + SS + EC + PT + (1|Participant), family=binomial, data=d_s)
summary(ea2.1)
r.squaredGLMM(ea2.1) 

# exploring 

# EC
ECEC = glm(Condition ~ EC, family = binomial, d_s)
summary(ECEC)
# PT
PTPT = glm(Condition ~ PT, family = binomial, d_s)
summary(PTPT)
# FS
FSFS = glm(Condition ~ FS, family = binomial, d_s)
summary(FSFS)
# PD 
PDPD = glm(Condition ~ PD, family = binomial, d_s)
summary(PDPD)
# SS
SSSS = glm(Condition ~ SS, family = binomial, d_s)
summary(SSSS)

# congruity
rtrt = lm(RTlog~ Congruity, data = d)
summary(rtrt)
# condition
concon = lm(RTlog~ Condition, data = d)
summary(concon)
# condition incongruent RTs
incon = lm(RTlog~ Condition, data = d_incongruent)
summary(incon)

```



# Bayesian
```{r}
df_1 = data.frame(d_s$Participant, d_s$Condition, d_s$Reaction_time, d$Congruity) 
library(brms)

rt_model <- brm(Reaction_time ~ 1 + Condition + Congruity + Condition*Congruity + (1|Participant), data = d_dot, prior = NULL, chains = 2, iter = 2000, cores = 2)
summary(rt_model)

rt_model1 <- brm(Reaction_time ~ 1 + Condition + Congruity + Condition*Congruity + (1|Participant), # Outcome as a function of the predictors as in lme4. 
               data=d_dot, # Define the data
               family=poisson(link=log), # Define the family. 
               iter = 5000, warmup = 200, cores = 4)
summary(brm_out1)
plot(brm_out1)


library(plyr)
df_1 = rename(df_1, c("d_s.Participant"="Participant", "d_s.Condition"="Condition", "d_s.Reaction_time"="Reaction_time"))
str(df_1)
df_1$Condition = as.numeric(df_1$Condition)
df_1$Condition = as.integer(df_1$Condition)

m1 <- rethinking::map(
  alist(
    Reaction_time ~ dnorm( mu , sigma ) , 
    mu <- ai + a[Participant] + bC*Condition,
    ai ~ dnorm(0, 1) , 
    a[Participant] ~ dnorm( 0 , 1 ) , 
    bC ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df_1)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
library(rethinking)
precis(m1)
plot(precis(m1))

df_1 = data.frame(d_s$Participant, d_s$Condition, d_s$Reaction_time, d_s$EC) 

library(plyr)
df_1 = rename(df_1, c("d_s.Participant"="Participant", "d_s.Condition"="Condition", "d_s.Reaction_time"="Reaction_time", "d_s.EC"="EC"))
str(df_1)
df_1$Condition = as.numeric(df_1$Condition)
df_1$Participant = as.numeric(df_1$Participant)

m8 <- map2stan( 
alist(
  Condition ~ dbinom( 1 , p ) , 
  logit(p) <- ai + a[Participant] + bE*EC + bR*Reaction_time + bO*EC*Reaction_time,
  ai ~ dnorm(0,1),
  a[Participant] ~ dnorm(0,1),
  bE ~ dnorm(0, 0.2),
  bR ~ dnorm(0, 0.2),
  bO ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_1 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m8)
precis(m8, depth = 2)
# devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m8))





```


```{r}

```

